### 2018-07-05 paper/4-build.tex
Tweak deep constructive traces

The deep constructive trace approach only works if the operations are
\emph{deterministic}, otherwise inconsistencies arise
(see~\S\ref{sec-non-determinism}). \simon{That section doesn't actually
  mention ``inconsistencies''.
  Also I think the inconsistencies are called Frankenbuilds, a term we might
  want to introduce.}
Concretely, if the result of building a key
given a set of immediate dependencies can vary, then it is possible that key
\hs{k} will have been computed locally, but something \emph{using} \hs{k} will
have been taken as a constructive input using a different value for \hs{k}. If
another rule combines those two values then two different values of \hs{k} will
have been used in one rule, leading to problems such as link-errors for typical
compilers.

>>>>

The deep constructive trace approach only works if the operations are
\emph{deterministic}, otherwise it is possible to violate correctness resulting
in a so-called ``Frankenbuild''~\cite{esfahani2016cloudbuild}. Concretely, if
the result of building a key given a set of immediate dependencies can vary,
then it is possible that key \hs{k} will have been computed locally, but
something \emph{using} \hs{k} will have been taken as a constructive input using
a different value for \hs{k}. If another rule combines those two values then two
different values of \hs{k} will have been used in one rule, leading to problems
such as link-errors for typical compilers.
